Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-20 ICML2019/main.tex
first pass section 4

@@

$\lexpmech$ shares candidate set and utility function with $\expmech$,
and outputs a result $r \in \mathcal{R}$ with probability:
\[
%\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
{\Pr}[z=r] = \frac
  {\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\]
where $LS(\dataobs)$ is the local sensitivity of the scoring function, defined as:
\begin{equation}\label{eq:local_sensitivity_scoring}
LS(\dataobs)\equiv\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert 
\end{equation}
The above can be proven to simplify to:
\begin{lem}
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\end{lem}
The interested reader can check the proof in the Appendix \ref{??}.

@@

\begin{thm}
  \label{thm_gamma_smooth}
  For any $\dataobs, \dataobs'\in\{0,1\}^n$, and $\gamma \in \mathbb{R}^{+}$
  if  $\adj{\dataobs}{\dataobs'}$ then $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
\end{thm}
The interested reader will find the proof in Appendix \ref{??}.
We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\[\frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
{\unomalizer{\dataobs}}.
\]
where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}

As already mentioned $\expmech, \lexpmech, \sexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
\[
  \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. {\color{red}{what is m here?}}

@@

\subsection{Privacy of Laplace Mechanism Family}
Mechanisms in Laplace family are $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.

@@

\subsubsection{$\lexpmech$ non-Differential Privacy}
Exponential mechanism with local sensitivity non-differential privacy.

@@

We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$), standard exponential mechanism ($\mathsf{expMech}$), non-private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).

@@

Candidates of smaller distance from true posterior are considered to be good results, which can result in good accuracy. From Fig. \ref{fig_theory}, it can be derived that all these mechanisms (except standard exponential mechanism $\expmech$ in green line) can output good results with larger probability. The $\lexpmech$ can output good results with higher probability than others, but $\lexpmech$ is non-private. For these are $\epsilon -$differentially private, the improved laplace mechanism $\ilapmech$ with $\ell_1$ norm metric can produce good results with higher probability, i.e., perform better in terms of accuracy than others. As the dimension increases from 2 to 3, mechanisms' behavior remain the same.

>>>>

It is possible to achieve $\epsilon$-differential privacy through use and composition of
a few basic components. Some of these components are now reviewed.

\noindent \emph{Laplace mechanism.}
The Laplace mechanism releases a random number drawn from the Laplace distribution with
mean $\mu=q(d)$ and scale $\nu$. Where $q$ is a numeric query on a database $d$.
If $\nu\geq \frac{\Delta_f}{\epsilon}$, with $\Delta_f=\displaystyle\max_{d,d':\adj{d}{d'}}{\lvert f(d_1)-f(d_2)\lvert}$
then the mechanism is $\epsilon$-differentially private as proven in \cite{???}.

\noindent \emph{Exponential mechanism.}

\noindent \emph{Composition.}

\noindent \emph{Postprocessing.}

@@

$\lexpmech$ shares candidate set and utility function with $\expmech$,
and outputs a result $r \in \mathcal{R}$ with probability:
\[
%\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
\frac
  {\exp(\frac{\epsilon \cdot u(x,r)}{2\cdot LS(\dataobs)})}
{\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot LS(\dataobs)})},
\]
where $LS(\dataobs)$ is the local sensitivity of the scoring function, defined as:
\begin{equation}\label{eq:local_sensitivity_scoring}
LS(\dataobs)\equiv\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert 
\end{equation}
The above can be proven to simplify to:
\begin{lem}
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\end{lem}
The interested reader can check the proof in the Appendix \ref{??}.

@@

\begin{thm}
  \label{thm_gamma_smooth}
  For any $\dataobs, \dataobs'\in\{0,1\}^n$, and $\gamma \in \mathbb{R}^{+}$
  if  $\adj{\dataobs}{\dataobs'}$ then $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
\end{thm}
The interested reader will find the proof in Appendix \ref{??}.
We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\[
  \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
  {\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{4\cdot S(\dataobs)})},
\]
where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}

As already mentioned $\expmech, \lexpmech, \hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
\[
  \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. {\color{red}{what is m here? and was $\datauni$} defined?}

@@

\subsection{Privacy of Laplace Mechanism Family}
The following lemmas prove the privacy of all the mechanisms (besides $\lexpmech$) presented so far.
Mechanisms $\lapmech$ and $\ilapmech$ are trivially $\epsilon$-differentially private since the mechanisms
add Laplacian noise proportional to the $\ell_1$-norm sensitivity to the arguments of the posterior distributions.
\begin{lem}
  $\lapmech$, $\ilapmech$ are $\epsilon$-differentially private.
\end{lem}

@@

% \subsubsection{$\lexpmech$ non-Differential Privacy}
% Exponential mechanism with local sensitivity non-differential privacy.

@@

We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$),
standard exponential mechanism ($\mathsf{expMech}$),
non private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).

@@

Candidates of smaller distance from true posterior are considered to be good results, which can result in good accuracy. From Fig. \ref{fig_theory}, it can be derived that all these mechanisms (except standard exponential mechanism $\expmech$ in green line) can output good results with larger probability. The $\lexpmech$ can output good results with higher probability than others, but $\lexpmech$ is non private. For these are $\epsilon -$differentially private, the improved laplace mechanism $\ilapmech$ with $\ell_1$ norm metric can produce good results with higher probability, i.e., perform better in terms of accuracy than others. As the dimension increases from 2 to 3, mechanisms' behavior remain the same.
